Classical Planning Algorithms ¡ on the Atari Video Games: Preliminary Results

### 2014-11-18 icaps15-paper/paper.tex
Experimental Section
* Corrected remark about experimental setup

We tested  $\IW(1)$ and \BFS\  over $9$ games: those considered in the \emph{training} set
of \cite{bellemare:jair2013}, abbreviated  as BNVB, and those discussed in \cite{deep-mind-atari}.
In Table~\ref{performance},  the performance of  $\IW(1)$ and \BFS\
% , characterized by the average score obtained over all episodes, the standard deviation
% of the score obtained and time (in seconds) per lookahead,
is compared with that of \UCT, breadth-first search (\BRFS), and random action selection.
The discount factor used by all the algorithms is $\gamma=0.995$ and the average scores
reported for \UCT\ in  BNVB  are included in  parenthesis for reference. 
Our experimental setup  follows the one in BNVB with two exceptions: rather than
considering $10$ runs per games, we considered just $5$ due to time constraints (*** ???),
and  a maximum budget of  $150,000$ simulated frames is applied to all the  algorithms, 
including  \UCT\ that is limited to  $500$ base policy rollouts of depth $300$.
% \footnote{In \UCT,  $500$ base policy rollouts
% of depth $300$ is equivalent to a budget of $150,000$ simulated frames.}.
The bound on the number of simulated frames is like a bound on lookahead time, 
as most of the time in the lookahead search is spent in the calls to the emulator
for computing the next RAM state.  Also in order to save time, as in BNVB,   all of the algorithms 
reuse the subtree from  the previous lookahead that is rooted in the selected
child, deleting its siblings and their descendants. More precisely, no calls to the
emulator are done  for transitions that are cached in that subtree. As a result
the number of nodes in the lookahead tree may be larger actually than the budget.
In addition, in  \IW, the states that are ``reused''  from the  previous searches
are ignored in the computation of the novelty of new states so that more states 
can  escape pruning. Otherwise, \IW\ often doesn't use the full budget. This is not 
needed in \BFS\ which does no pruning.  $\IW(1)$ and \BFS\ have been  limited 
search up to a depth of $m=1500$  frames and up to $m=20,000$ frames per root branch.
This is to avoid the search for going too deep or being too committed to a single
root action. (**** Please revise ****).

>>>>

We tested  $\IW(1)$ and \BFS\  over $9$ games: those considered in the \emph{training} set
of \cite{bellemare:jair2013}, abbreviated  as BNVB, and those discussed in \cite{deep-mind-atari}.
In Table~\ref{performance},  the performance of  $\IW(1)$ and \BFS\
% , characterized by the average score obtained over all episodes, the standard deviation
% of the score obtained and time (in seconds) per lookahead,
is compared with that of \UCT, breadth-first search (\BRFS), and random action selection.
The discount factor used by all the algorithms is $\gamma=0.995$ and the average scores
reported for \UCT\ in  BNVB  are included in  parenthesis for reference. 
Our experimental setup  follows the one in BNVB with one exception: a maximum budget of  $150,000$ simulated frames 
is applied to all the  algorithms, including  \UCT\ that is limited to  $500$ base policy rollouts of depth $300$.
% \footnote{In \UCT,  $500$ base policy rollouts
% of depth $300$ is equivalent to a budget of $150,000$ simulated frames.}.
The bound on the number of simulated frames is like a bound on lookahead time, 
as most of the time in the lookahead search is spent in the calls to the emulator
for computing the next RAM state.  Also in order to save time, as in BNVB,   all of the algorithms 
reuse the subtree from  the previous lookahead that is rooted in the selected
child, deleting its siblings and their descendants. More precisely, no calls to the
emulator are done  for transitions that are cached in that subtree. As a result
the number of nodes in the lookahead tree may be larger actually than the budget.
In addition, in  \IW, the states that are ``reused''  from the  previous searches
are ignored in the computation of the novelty of new states so that more states 
can  escape pruning. Otherwise, \IW\ often doesn't use the full budget. This is not 
needed in \BFS\ which does no pruning.  $\IW(1)$ and \BFS\ have been  limited 
search up to a depth of $m=1500$  frames and up to $m=20,000$ frames per root branch.
This is to avoid the search for going too deep or being too committed to a single
root action. (**** Please revise ****).
